Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2011-10-18 article.tex
Another minor edit
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1408 ccdd05d5-56c1-461a-bf98-85f6876523b4

However, the resulting filters are still not
orthogonal across the parameter space, and are in fact highly redundant.
We use the \SVD\ to approximate the template bank by a set of orthogonal
\emph{basis filters}~\citep{Cannon:2010p10398}.  We find that this approximation
reduces the number of filters needed by another factor of $\sim$100.  These two
transformations combined reduce the number of floating point operations
to the level that is competitive with the conventional high-latency \FD\
matched filter approach.  In the remainder of this section we describe the
\lloid\ algorithm in detail and provide some basic computational cost scaling.

>>>>

However, the resulting filters are still not
orthogonal across the parameter space, and are in fact highly redundant.
We use the \SVD\ to approximate the template bank by a set of orthogonal
\emph{basis filters}~\citep{Cannon:2010p10398}.  We find that this approximation
reduces the number of filters needed by another factor of $\sim$100.  These two
transformations combined reduce the number of floating point operations
to a level that is competitive with the conventional high-latency \FD\
matched filter approach.  In the remainder of this section we describe the
\lloid\ algorithm in detail and provide some basic computational cost scaling.
